On the probability of finding nonphysical solutions through shadowing\tnoteref{1}

### 2020-12-12 main_els.tex
Shadowing second para

The analysis of the long-term behavior of {\em shadowing} solutions in the majority of the chaotic models constructed in this paper reveals that shadowing solutions are almost surely {\em nonphysical}: they do not represent the behavior of a physically observed solution starting almost everywhere. This also leads us to the conclusion that shadowing-based sensitivities \cite{qiqi-lss} of long-time averages to parameter changes can be incorrect. Thus, the main conjecture of this paper urges us to reconsider the use of chaotic numerical simulations, and statistical sensitivity analysis on these simulations. These implications are particularly important for climate studies, where chaotic models are widely used to make long-term predictions. In particular, three implications of the evidence in this paper may be stated, the third of which harnesses the statistical inconsistency between slightly different models:

@@

>>>>

We refer to the statistically mismatched shadowing solutions as {\em nonphysical} solutions since they do not represent the behavior of a physically observed solution starting almost everywhere. We identify different ways in which nonphysical solutions occur, adding to the known examples such as periodic orbits embedded within a chaotic attractor. The shadowing lemma \cite{anosov}\cite{bowen} establishes the existence of shadowing orbits corresponding to small perturbations but does not preclude the possibility of nonphysical shadowing orbits (\cite{katok} Theorem 18.1.2).

@@

This also leads us to the conclusion that shadowing-based sensitivities \cite{qiqi-lss} of long-time averages to parameter changes can be incorrect. Thus, the main conjecture of this paper urges us to reconsider the use of chaotic numerical simulations, and statistical sensitivity analysis on these simulations. These implications are particularly important for climate studies, where chaotic models are widely used to make long-term predictions. In particular, three implications of the evidence in this paper may be stated, the third of which harnesses the statistical inconsistency between slightly different models:
